Automated topic naming to support analysis of software maintenance activities

### 2010-08-21 icse/icse2011.tex
annotation observations
summary of techniques
understanding software ...

As noted in Section \ref{sec:wordlist}, each topic in our data-set can be composed of zero, one, or more NFRs. 
For example, a commit message might address \textit{reliability} in the context of \textit{efficiency}, or make a \textit{maintainability} improvement in the source code that related to \textit{usability}. 
However, traditional machine learning techniques, such as naive Bayes, can only map topics to a single class. 
The Mulan~\cite{mulan} library encapsulates several different multi-label machine learners which can label elements with multiple labels.
Mulan also includes methods for determining the performance of such techniques.
% TOO DETAILED The problem framed in the learners above has changed; instead of looking at the precision and recall of applying one label, we rank multiple labels at once. We must check if the full subset of labels was applied, and then how much of that subset was applied.

@@

Figure~\ref{fig:mulan} presents the results of Mulan's best multi-label learners for our data. 
Calibrated Label Ranking (CLR) is a learner that builds two layers, the first layer determines if an entity should be labelled, while the second layer determines what labels should be assigned.
The Hierarchy Of Multi-label classifiERs (HOMER) and Binary Relevance (BR) act as a hierarchy of learners: BR is flat, while HOMER tries to build a deeper hierarchy to build a more accurate learner~\cite{mulan}. 
These classifiers performed better than other multi-label classifiers as they have the best micro and macro ROC scores. 
The multi-label and single-label learners had similar performance: for MySQL, BR and NaiveBayes had similar macro-ROC scores of $0.74$.
% although their results are comparable to the naive Bayesian learners we used in Section \ref{sec:suplabelling}.
%\todo[inline]{discuss this similarity in more detail}

@@

\section{Understanding software maintenance activities} 
\label{sec:analysis}
% \todo[inline]{talk about this topic in one section}
% \todo[inline]{reference project name Nomen more}
Since our ROC values produced acceptable results, we now turn to \emph{applying} those techniques to understand software maintenance activities. We evaluated two research questions:
\begin{enumerate}
\item Do label frequencies change over time? That is, is a certain quality of more interest at one point in the life-cycle than some other? 
\item  Do the different projects differ in their relative topic interest? That is, is a particular quality more important to one project than the other projects?  
\end{enumerate}

>>>>

As noted in Section \ref{sec:wordlist}, each topic in our data-set can be composed of zero, one, or more NFRs. 
For example, a commit message might address \textit{reliability} in the context of \textit{efficiency}, or make a \textit{maintainability} improvement in the source code that related to \textit{usability}. 
However, traditional machine learning techniques, such as Naive Bayes, can only map topics to a single class. 
The Mulan~\cite{mulan} library encapsulates several different multi-label machine learners which can label elements with multiple labels.
Mulan also includes methods for determining the performance of such techniques.
% TOO DETAILED The problem framed in the learners above has changed; instead of looking at the precision and recall of applying one label, we rank multiple labels at once. We must check if the full subset of labels was applied, and then how much of that subset was applied.

@@

Figure~\ref{fig:mulan} presents the results of Mulan's best multi-label learners for our data. 
Calibrated Label Ranking (CLR) is a learner that builds two layers, the first layer determines if an entity should be labelled, while the second layer determines what labels should be assigned.
The Hierarchy Of Multi-label classifiERs (HOMER) and Binary Relevance (BR) act as a hierarchy of learners: BR is flat, while HOMER tries to build a deeper hierarchy to build a more accurate learner~\cite{mulan}. 
These classifiers performed better than other multi-label classifiers as they have the best micro and macro ROC scores. 
The multi-label and single-label learners had similar performance: for MySQL, BR and NaiveBayes had similar macro-ROC scores of $0.74$.
% although their results are comparable to the naive Bayesian learners we used in Section \ref{sec:suplabelling}.
% \todo[inline]{discuss this similarity in more detail}

@@

\section{Understanding software maintenance activities} 
\label{sec:analysis}
% \todo[inline]{talk about this topic in one section}
% \todo[inline]{reference project name Nomen more}
Since our ROC values produced acceptable results, we now turn to \emph{applying} those techniques to understand software maintenance activities. We evaluated two research questions:
\begin{enumerate}
\item Do label frequencies change over time? Is a certain quality of more interest at one point in the life-cycle than some other? 
\item  Do the different projects differ in their relative topic interest? Is a particular quality more important to one project than the other projects?  
\end{enumerate}
